Binary Image Transition State Search Method

### 2022-03-31 manuscript.tex
Removed SI footnote

\subsection{BITSS: Constraint coefficients}
To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
\begin{gather}
  \kappa_e = \frac {\alpha} {2 E_B},
  \label{eq:ke}
  \\
  \kappa_d = \max \left(
    \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
    \frac{E_B}{\beta d_i^2} \right),
  \label{eq:kd}
\end{gather}
where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, and extra details for the example systems}).
Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.

@@

% %\bibliography{../../library.bib}

@@

\begin{thebibliography}{46}%

@@

\bibitem [{Note1()}]{Note1}%
  \bibinfo {note} {See Supplemental Material at [URL] for derivations of the
  constraint coefficients, extra details for the example systems, results for
  the speed test against DNEB, and a comparison of the discontinuous energy
  landscape with the standard Lennard-Jones cluster}\BibitemShut {NoStop}%

>>>>

\subsection{BITSS: Constraint coefficients}
To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
\begin{gather}
  \kappa_e = \frac {\alpha} {2 E_B},
  \label{eq:ke}
  \\
  \kappa_d = \max \left(
    \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
    \frac{E_B}{\beta d_i^2} \right),
  \label{eq:kd}
\end{gather}
where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.

@@

% % \bibliography{../../library.bib}

@@

\begin{thebibliography}{45}%

@@
